\cvsection{About me}
I want the world to be better because I was here. And I think engineering gives us
both the required tools and skills to achieve it.

\divider

Nova Member -- top 3\% of talent in the industry.

\divider

{\begin{quote}\normalsize
``Scientists study the world as it is, engineers create the world that never has been.'' -- Theodore von Karman
\end{quote}}

% I am a passionate engineer with experience in R\&D, full-stack development, and higher education. I am currently working as an R\&D engineer at Teldat S.A., developing the NGFW used by all brand-new products. Additionally, I am a member of Nova, a merit-based access network for top talent to connect and accelerate their careers. I have also worked as a higher education professor, teaching subjects such as ISO and PSP, and mentoring student projects. As a full-stack developer, I have worked on several private projects, including the ADAF project developed for Saturno Labs. I have also been involved in various tech conferences as a speaker, organizer, and volunteer coordinator. I am highly skilled in Python, SQL, Shell, hardware, Android development, NodeJS, embedded systems, and DevOps. I hold a master's degree in International Leadership and an MSc. in Distributed and Embedded Systems Software, as well as a BSc. in Computer Science. I am a self-motivated individual who is constantly learning and strives for excellence in all of my endeavors.

\cvsection{\textit{Soft skills}}

\cvachievement{\faStar}{Excellence}{%
I always do my best, and I trust the rest of the team to do the same to reach our objectives together
}

\divider

\cvachievement{\faGraduationCap}{Learning}{%
We never stop learning, and I have assumed this dogma as a habit and hobby.
}

\divider

\cvachievement{\faMale}{\textit{Tech} Inspiration}{%
Even though I am young, I work with some of the most outstanding tech professionals, organize some
conferences in my country, and do talks at many others.
}

\cvsection{\textit{Hard Skills}}

\cvtag{Python}
\cvtag{Android (Kotlin, Java)}
\cvtag{C/C++}
\cvtag{SQL}
\cvtag{NodeJS}
\cvtag{Embebidos}
\cvtag{MQTT}
\cvtag{Shell}
\cvtag{Linux}
\cvtag{DevOps}
\cvtag{Docker}
\cvtag{Git}
\cvtag{\textit{Hardware}}
\cvtag{\LaTeX{}}
\cvtag{LibreOffice / MS Office}

\cvsection{Education}

\cvevent{Ms. in International Leadership}{\accentsub{https://frdelpino.es/}{Fundación Rafael del Pino}, \accentsub{https://clytupm.es/master-internacional-en-liderazgo-upm/}{Universidad Politécnica de Madrid}}{Sept. 2021 -- May 2023}{}
% \divider
\cvevent{MSc. in Distributed and Embedded Systems Software}{\accentsub{https://msde.etsisi.upm.es/}{Universidad Politécnica de Madrid}}{Sept. 2020 -- July 2021}{}
% \divider
\cvevent{BSc. in Computer Science}{\accentsub{https://www.etsisi.upm.es/estudios/grados/61ci/ig}{Universidad Politécnica de Madrid}}{Sept. 2016 -- Nov. 2020}{}
